Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-12-11 Manuscript.Rmd
This works, but the pdf isn't opening well

---
title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
author: "Claudio Toro-Serey^1^ & Joseph T. McGuire^1^"
output:
  word_document: 
    reference_docx: Style_reference.docx
  pdf_document: default
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

``` {r ROI computation from Matlab, echo=FALSE, message = FALSE}
# This version is literally what I had selected originally, plus 25, OFC, 10v, and RSC; 
# Minus PGi and PGs. This replicates the 7m finding. 
# But if I add L_s32 in accord with our meeting on 12/4/18, then that's significant too
Yeo_labels <- c("L_25_ROI",
                "L_OFC_ROI",
                "L_10v_ROI",
                "R_25_ROI",
                "R_OFC_ROI",
                "R_10v_ROI",
                "L_s32_ROI",
                "L_RSC_ROI",
                "R_RSC_ROI",
                "R_8Ad_ROI",
                "R_9p_ROI",
                "R_23d_ROI",
                "R_d23ab_ROI",
                "R_31a_ROI",
                "R_31pv_ROI",
                "R_31pd_ROI",
                "R_7m_ROI",
                "R_v23ab_ROI",
                "R_p24_ROI",
                "R_d32_ROI",
                "R_9m_ROI",
                "R_p32_ROI",
                "R_a24_ROI",
                "R_10r_ROI",
                "R_10d_ROI",
                "L_8Ad_ROI",
                "L_9p_ROI",
                "L_23d_ROI",
                "L_d23ab_RO",
                "L_31a_ROI",
                "L_31pv_ROI",
                "L_31pd_ROI",
                "L_7m_ROI",
                "L_v23ab_ROI",
                "L_p24_ROI",
                "L_d32_ROI",
                "L_9m_ROI",
                "L_p32_ROI",
                "L_a24_ROI",
                "L_10r_ROI",
                "L_10d_ROI",
                "R_s32_ROI",
                "R_9a_ROI",
                "L_p10p_ROI",
                "L_PCV_ROI")

@@

# # Permutation analysis
# # Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
# # Load the coordinates as studies in a list, because for the contrast the studies are permuted
# # Use table(unlist(list)) to get the counts in that case
# setwd('./DEC')
# templist <- dir()
# studyList_sv <- lapply(templist, readr::read_csv, col_names = F)
# 
# setwd('../DMN/')
# templist <- dir()
# studyList_dmn <- lapply(templist, readr::read_csv, col_names = F)
# 
# # For each permutation, reassign the study labels, maintaining the original number of studies per condition 
# allStudies <- c(studyList_sv, studyList_dmn)
# nPerms <- 5000
# nullDist <- numeric()
# 
# for (i in seq(nPerms)) {
#   
#   if(i %in% c(nPerms*0.25, nPerms*0.5, nPerms*0.75, nPerms*0.95)) {print(paste("Completed", i/nPerms, "percent of the permutation..."))}
#     
#   # Sample all the studies and divide into 2 groups
#   randPerm <- sample(allStudies)
#   tmpSV <- randPerm[seq(length(studyList_sv))]
#   tmpDMN <- randPerm[-seq(length(studyList_sv))]
#   
#   # Count the number of times each region was reported in the literature
#   # Bilateral activations still count as 1, so we might want to reconsider that
#   tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
#                       SV = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpSV))}),
#                       DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpDMN))}))
#   
#   # Perform the prop test for each pair and get the max chi-squared stat
#   nullDist[i] <- max(
#                   apply(tmpDF[,2:3], 1, function(data) {
#                     prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
#                     }
#                   ), na.rm = T)
#   
# }
# 
# # Now do the same for the actual data, to see how it compares to the null dist
# tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
#                     SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
#                     DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
#                     propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
#                     propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
# 
# # Perform the prop test for each pair and get the max chi-squared stat + pvalue based on the computed null distribution
# tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {
#   round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)
#   })
# tmpDF$Pval <- 1 - ecdf(nullDist)(tmpDF$Chi_squared) # probability of finding a chi-squared stat at least as large as the observed under a permuted null distribution
# 
# # ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
# significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist,0.95))

@@

``` {r ROI computation, echo=FALSE, message = FALSE}
# #TO DO: CHANGE THIS SO IT'S BASED ON STUDYLIST_SV/DMN, COUNTING JUST LIKE IN THE PERMUTATION ABOVE
# ## ROI definition
# # First, load the raw count csv files
# valCounts <- read.csv2('decCounts.csv', sep = ",")
# dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")
# 
# # Then, get the means of the counts per domain, both within/outside the search space
# # This is to get a broad estimate of the average report amounts in the literature
# tempBoot <- bootstrap(valCounts$Counts)
# BV <- round(mean(tempBoot))
# BVquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
# tempBoot <- bootstrap(dmnCounts$Counts)
# BD <- round(mean(tempBoot))
# BDquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
# rm(tempBoot)
# 
# # Now select only the ROIs from Yeo et al (TEMP)
# valCounts <- getCoords(Labels = Yeo_labels, Coords = valCounts)$Coords
# dmnCounts <- getCoords(Labels = Yeo_labels, Coords = dmnCounts)$Coords
# 
# # Now, for every ROI, do a prop test to check if the proportion of reports is significantly greater
# # than the mean report over the number of studies (i.e. sample-based null probability, which could be changed to perm)
# for (i in seq(valCounts$Counts)) {
#   indx <- valCounts$Counts[i]
#   tempTest <- prop.test(indx, 27, alternative = "greater", p = BV/27)
#   valCounts$Chi[i] <- tempTest$statistic
#   valCounts$pVal[i] <- tempTest$p.value
# }
# 
# for (i in seq(dmnCounts$Counts)) {
#   indx <- dmnCounts$Counts[i]
#   tempTest <- prop.test(indx, 77, alternative = "greater", p = BD/77)
#   dmnCounts$Chi[i] <- tempTest$statistic
#   dmnCounts$pVal[i] <- tempTest$p.value
# }
# 
# # Retain only the significant parcels
# t1 <- valCounts$Label[valCounts$pVal < 0.05]
# t2 <- dmnCounts$Label[dmnCounts$pVal < 0.05]
# 
# # Remove hemispheric references
# t1 <- unique(substring(t1,2))
# t2 <- unique(substring(t2,2))
# 
# # Labels to put in text
# dmnLbls <- gsub("ROI","", t2) 
# dmnLbls <- gsub("_","", dmnLbls)
# valLbls <- gsub("ROI","", t1) 
# valLbls <- gsub("_","", valLbls)
# 
# # final overlap
# bothLbls <- dmnLbls[dmnLbls %in% valLbls]

# This part is just for reference, as the labels are loaded from a file
# # And get the set of overlapping areas between literatures
# # This is missing some cingulate and PFC areas, and adds V2.
# # However, we can say that we are filling in the gap for completeness,
# # and removing V2 because it's demonstrably irrelevant.
# bothLbls <- unique(c(t1[t1 %in% t2], t2[t2 %in% t1]))
# 
# # You could also try to permute the allocation of reports per literature,
# # and then perform a chi-squared per parcel. Get the max stat per iteration.
# # Now you have your null distribution.

@@

#grid.arrange(pcc1,pfc1, ncol = 2)
#grid.arrange(All,pcc2,pfc2, ncol = 1)

@@

### *Partition Comparison:Thresholded Full Datasets*
``` {r Partition comparison: all 2, echo=FALSE, message = FALSE, cache = TRUE}
# Apply threshold to Summaries
if (threshMaps) {
  for (i in seq(nSubj)) {
  Summaries[[i]] <- Summaries[[i]] %>%
    mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i,2]) & FiedlerVec < as.numeric(threshDF[i,3]), 0, FiedlerVec)) %>%
    mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
  }
}

@@

``` {r Partition comparison: halves, echo=FALSE, message = FALSE, cache = TRUE}
# Load data
setwd('./Summary_halves/')
temp <- list.files(pattern = "*_finalSummary.csv")
subjList_halves <- sapply(temp, substring, first=1, last=9)
Summaries_halves <- lapply(temp, read.csv)

@@

# Select subsection of subjects for plotting the similarity matrices
selectSubj <- seq(1,20)
Summaries_halves_plot <- Summaries_halves[selectSubj]
subjList_halves_plot <- subjList_halves[selectSubj]

# Load the correlation-based maps (this might be ok to move to the cor vs comm chunk)
temp <- list.files(pattern = "*_corHalves.csv")
Correlation_halves <- lapply(temp, read.csv, header = F)
Correlation_halves_plot <- Correlation_halves[selectSubj]

# Compare all halves with RI (plot only)
RI_all_between_halves_plot <- comparePartitions(Data = Summaries_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)

# Compare PCC and PFC among all subjects (plot only)
tempComm_PCC_halves_plot <- lapply(Summaries_halves_plot, "[", i = posteriorIndx, j =)
tempComm_PFC_halves_plot <- lapply(Summaries_halves_plot, "[", i = !posteriorIndx, j =)
RI_PFC_halves_plot <- comparePartitions(Data = tempComm_PFC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
RI_PCC_halves_plot <- comparePartitions(Data = tempComm_PCC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
```

@@

@@

# Select 10 subjects from the sample to plot
selectSubj <- seq(1,40)
subjList_sess_plot <- subjList_sess[selectSubj]
Summaries_sess_plot <- Summaries_sess[selectSubj]

# Across subjects (just for plotting)
RI_all_between_sess_plot <- comparePartitions(Data = Summaries_sess_plot, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
tempComm_PCC_sess <- lapply(Summaries_sess_plot, "[", i = posteriorIndx, j =)
tempComm_PFC_sess <- lapply(Summaries_sess_plot, "[", i = !posteriorIndx, j =)
RI_PFC_sess_plot <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
RI_PCC_sess_plot <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
```

@@

@@

``` {r Correlation vs community detection: compute, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
## Between halves analysis for correlation and communities (mPFC only)
tempComm_PFC_halves_plot <- lapply(seq_along(tempComm_PFC_halves_plot), function(x) cbind(tempComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
D1 <- tempComm_PFC_halves_plot
D2 <- lapply(tempComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
Data <- c(D1,D2)
allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))
```

@@

# Compare correlation with community approach on mPFC
tempComm <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, tempComm_PFC_halves[[x+1]]$FiedlerVec))
tempCor <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
tempBoth <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))
prepostComp <- data.frame(Community = tempComm, Correlation = tempCor, Between = tempBoth)
prepostComp <- melt(prepostComp)
colnames(prepostComp) <- c("Approach", "Correlation")
prepostComp_permTest <- permute(tempComm, tempCor, paired = T)
prepostComp_ES <- cohenD(tempComm, tempCor)
```

@@

### *Table 1. Significant brain regions per literature*
| Literature                  | Significant Brain Regions   |
| :-------------------------- | --------------------------: |
| Default Mode Network        | `r paste(dmnLbls)`          |
| Subjective Value            | `r paste(valLbls)`          |

@@

``` {r Stability per subject: PCC vs mPFC (Fig 10), fig.align="center", fig.width=10, fig.height=4, fig.cap = "Figure 10. ARI between each window and the original pattern for PCC and mPFC separately (left), and the mean per-subject ARI for the whole group (middle). Regardless of the mean ARI, standard deviation remained low for both regions (right).", echo=FALSE, message = FALSE, cache = TRUE}

# plots
SC_PCCPFC_plot <- ggplot(data = SC_PCC)
SC_PCCPFC_plot <- SC_PCCPFC_plot + geom_line(aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[2], alpha = 0.3, show.legend = F) +
  geom_smooth(aes(x = Window, y = Index), color = Cols[2], fill = Cols[2]) +
  ylim(0,1) + 
  labs(y = "ARI") +
  theme(text = element_text(size=35)) +
  geom_line(data = SC_PFC, aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[1], alpha = 0.3, show.legend = F) +
  geom_smooth(data = SC_PFC, aes(x = Window, y = Index), color = Cols[1], fill = Cols[1]) +
  theme_classic()

@@

grid.arrange(SC_PCCPFC_plot, SC_PCCPFC_mean_plot, SC_PCCPFC_sd_plot, ncol = 3)
```

>>>>

---
title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
author: "Claudio Toro-Serey^1^ & Joseph T. McGuire^1^"
output:
  pdf_document: default
  word_document: 
    reference_docx: Style_reference.docx
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

``` {r ROI computation from Matlab, echo=FALSE, message = FALSE, cache = TRUE}
# This version is literally what I had selected originally, plus 25, OFC, 10v, and RSC; 
# Minus PGi and PGs. This replicates the 7m finding. 
# But if I add L_s32 in accord with our meeting on 12/4/18, then that's significant too
Yeo_labels <- c("L_25_ROI",
                "L_OFC_ROI",
                "L_10v_ROI",
                "R_25_ROI",
                "R_OFC_ROI",
                "R_10v_ROI",
                "L_s32_ROI",
                "L_RSC_ROI",
                "R_RSC_ROI",
                "R_8Ad_ROI",
                "R_9p_ROI",
                "R_23d_ROI",
                "R_d23ab_ROI",
                "R_31a_ROI",
                "R_31pv_ROI",
                "R_31pd_ROI",
                "R_7m_ROI",
                "R_v23ab_ROI",
                "R_p24_ROI",
                "R_d32_ROI",
                "R_9m_ROI",
                "R_p32_ROI",
                "R_a24_ROI",
                "R_10r_ROI",
                "R_10d_ROI",
                "L_8Ad_ROI",
                "L_9p_ROI",
                "L_23d_ROI",
                "L_d23ab_RO",
                "L_31a_ROI",
                "L_31pv_ROI",
                "L_31pd_ROI",
                "L_7m_ROI",
                "L_v23ab_ROI",
                "L_p24_ROI",
                "L_d32_ROI",
                "L_9m_ROI",
                "L_p32_ROI",
                "L_a24_ROI",
                "L_10r_ROI",
                "L_10d_ROI",
                "R_s32_ROI",
                "R_9a_ROI",
                "L_p10p_ROI",
                "L_PCV_ROI")

@@

# Permutation analysis
# Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
# Load the coordinates as studies in a list, because for the contrast the studies are permuted
# Use table(unlist(list)) to get the counts in that case
# setwd('./DEC')
# templist <- dir()
# studyList_sv <- lapply(templist, readr::read_csv, col_names = F)
# 
# setwd('../DMN/')
# templist <- dir()
# studyList_dmn <- lapply(templist, readr::read_csv, col_names = F)
# 
# # For each permutation, reassign the study labels, maintaining the original number of studies per condition
# allStudies <- c(studyList_sv, studyList_dmn)
# nPerms <- 1000 # stored statistics are computed @ 5k, but it's computationally demanding to do that.
# nullDist <- numeric()
# 
# for (i in seq(nPerms)) {
# 
#   if(i %in% c(nPerms*0.25, nPerms*0.5, nPerms*0.75, nPerms*0.95)) {print(paste("Completed", i/nPerms, "percent of the permutation..."))}
# 
#   # Sample all the studies and divide into 2 groups
#   randPerm <- sample(allStudies)
#   tmpSV <- randPerm[seq(length(studyList_sv))]
#   tmpDMN <- randPerm[-seq(length(studyList_sv))]
# 
#   # Count the number of times each region was reported in the literature
#   # Bilateral activations still count as 1, so we might want to reconsider that
#   tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
#                       SV = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpSV))}),
#                       DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpDMN))}))
# 
#   # Perform the prop test for each pair and get the max chi-squared stat
#   nullDist[i] <- max(
#                   apply(tmpDF[,2:3], 1, function(data) {
#                     prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
#                     }
#                   ), na.rm = T)
# 
# }
# 
# # Now do the same for the actual data, to see how it compares to the null dist
# tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
#                     SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
#                     DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
#                     propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
#                     propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
# 
# # Perform the prop test for each pair and get the max chi-squared stat + pvalue based on the computed null distribution
# tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {
#   round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)
#   })
# tmpDF$Pval <- 1 - ecdf(nullDist)(tmpDF$Chi_squared) # probability of finding a chi-squared stat at least as large as the observed under a permuted null distribution
# 
# # ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
# significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist,0.95))

@@

``` {r ROI computation, echo=FALSE, message = FALSE}
#TO DO: CHANGE THIS SO IT'S BASED ON STUDYLIST_SV/DMN, COUNTING JUST LIKE IN THE PERMUTATION ABOVE
## ROI definition
# First, load the raw count csv files
valCounts <- read.csv2('decCounts.csv', sep = ",")
dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")

# Then, get the means of the counts per domain, both within/outside the search space
# This is to get a broad estimate of the average report amounts in the literature
tempBoot <- bootstrap(valCounts$Counts)
BV <- round(mean(tempBoot))
BVquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
tempBoot <- bootstrap(dmnCounts$Counts)
BD <- round(mean(tempBoot))
BDquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
rm(tempBoot)

# Now select only the ROIs from Yeo et al (TEMP)
valCounts <- getCoords(Labels = Yeo_labels, Coords = valCounts)$Coords
dmnCounts <- getCoords(Labels = Yeo_labels, Coords = dmnCounts)$Coords

# Now, for every ROI, do a prop test to check if the proportion of reports is significantly greater
# than the mean report over the number of studies (i.e. sample-based null probability, which could be changed to perm)
for (i in seq(valCounts$Counts)) {
  indx <- valCounts$Counts[i]
  tempTest <- prop.test(indx, 27, alternative = "greater", p = BV/27)
  valCounts$Chi[i] <- tempTest$statistic
  valCounts$pVal[i] <- tempTest$p.value
}
for (i in seq(dmnCounts$Counts)) {
 indx <- dmnCounts$Counts[i]
 tempTest <- prop.test(indx, 77, alternative = "greater", p = BD/77)
 dmnCounts$Chi[i] <- tempTest$statistic
 dmnCounts$pVal[i] <- tempTest$p.value
}
# Retain only the significant parcels
t1 <- valCounts$Label[valCounts$pVal < 0.05]
t2 <- dmnCounts$Label[dmnCounts$pVal < 0.05]
# Remove hemispheric references
t1 <- unique(substring(t1,2))
t2 <- unique(substring(t2,2))
# Labels to put in text
dmnLbls <- gsub("ROI","", t2)
dmnLbls <- gsub("_","", dmnLbls)
valLbls <- gsub("ROI","", t1)
valLbls <- gsub("_","", valLbls)

#bothLbls <- dmnLbls[dmnLbls %in% valLbls] # This part is just for reference, as the labels are loaded from a file
# final overlap
# And get the set of overlapping areas between literatures
# This is missing some cingulate and PFC areas, and adds V2.
# However, we can say that we are filling in the gap for completeness,
# and removing V2 because it's demonstrably irrelevant.
#bothLbls <- unique(c(t1[t1 %in% t2], t2[t2 %in% t1]))
# You could also try to permute the allocation of reports per literature,
# and then perform a chi-squared per parcel. Get the max stat per iteration.
# Now you have your null distribution.

@@

#grid.arrange(pcc1,pfc1, ncol = 2)
#grid.arrange(ecdfALL,ecdfPCC,ecdfPFC, ncol = 1)

@@

### *Partition Comparison:Thresholded Full Datasets*
``` {r Partition comparison: all thresholded, echo=FALSE, message = FALSE, cache = TRUE}
# Apply threshold to Summaries
if (threshMaps) {
  for (i in seq(nSubj)) {
  Summaries[[i]] <- Summaries[[i]] %>%
    mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i,2]) & FiedlerVec < as.numeric(threshDF[i,3]), 0, FiedlerVec)) %>%
    mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
  }
}

@@

``` {r Partition comparison: halves, echo=FALSE, message = FALSE, cache = TRUE}
# Load data
setwd('./Summary_halves/')
temp <- list.files(pattern = "*_finalSummary.csv")
subjList_halves <- sapply(temp, substring, first=1, last=9)
Summaries_halves <- lapply(temp, read.csv)
selectSubj <- seq(20)

# Before thresholding, capture within/between daily comparisons for FV vs correlation analysis (only for daily)
# Select a subsection of participants for plotting
Summaries_halves_plot <- Summaries_halves[selectSubj]
unthreshComm_PFC_halves_plot <- lapply(Summaries_halves_plot, "[", i = !posteriorIndx, j =)
unthreshComm_PFC_halves <- lapply(Summaries_halves, "[", i = !posteriorIndx, j =)

@@

# # Now recompute so that all network analyses are performed on thresholded data
# # Select subsection of subjects for plotting the similarity matrices
# Summaries_halves_plot <- Summaries_halves[selectSubj]
# subjList_halves_plot <- subjList_halves[selectSubj]

# # Compare all halves with RI (plot only)
# RI_all_between_halves_plot <- comparePartitions(Data = Summaries_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
# 
# # Compare PCC and PFC among all subjects (plot only)
# tempComm_PCC_halves_plot <- lapply(Summaries_halves_plot, "[", i = posteriorIndx, j =)
# tempComm_PFC_halves_plot <- lapply(Summaries_halves_plot, "[", i = !posteriorIndx, j =)
# RI_PFC_halves_plot <- comparePartitions(Data = tempComm_PFC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
# RI_PCC_halves_plot <- comparePartitions(Data = tempComm_PCC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
```

@@

# Select a submatrix with the best-performing subjects to show on the matrix figures
# These will be also displayed on the session matrix
# This way I don't have to recompute stuff
tmp <- data_frame(SubjID = subjList,
                  DailyARI = Halves_PFCComparison[[1]])
best <- tmp %>% top_n(10, wt = DailyARI) %>% arrange(DailyARI)
bestindx <- substr(subjList_halves,1,6) %in% best$SubjID

RI_all_between_halves_plot <- RI_all_between_halves[bestindx, bestindx]
RI_PFC_halves_plot <- RI_PFC_halves[bestindx, bestindx]
RI_PCC_halves_plot <- RI_PCC_halves[bestindx, bestindx]

# Load the correlation-based maps (this might be ok to move to the cor vs comm chunk)
temp <- list.files(pattern = "*_corHalves.csv")
Correlation_halves <- lapply(temp, read.csv, header = F)
Correlation_halves_plot <- Correlation_halves[bestindx] # CHANGE TO THE ACTUAL SUBJECTS
```

@@

# # Select 10 subjects from the sample to plot
# selectSubj <- seq(40)
# subjList_sess_plot <- subjList_sess[selectSubj]
# Summaries_sess_plot <- Summaries_sess[selectSubj]
# 
# 
# # Across subjects (just for plotting)
# RI_all_between_sess_plot <- comparePartitions(Data = Summaries_sess_plot, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
# tempComm_PCC_sess <- lapply(Summaries_sess_plot, "[", i = posteriorIndx, j =)
# tempComm_PFC_sess <- lapply(Summaries_sess_plot, "[", i = !posteriorIndx, j =)
# RI_PFC_sess_plot <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
# RI_PCC_sess_plot <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
```

@@

# Select the best performing for plotting, from daily performance
bestindx <- substr(subjList_sess,1,6) %in% best$SubjID
RI_all_between_sess_plot <- RI_all_between_sess[bestindx, bestindx]
RI_PFC_sess_plot <- RI_PFC_sess[bestindx, bestindx]
RI_PCC_sess_plot <- RI_PCC_sess[bestindx, bestindx]
```

@@

``` {r Correlation vs community detection: compute, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
## Between halves analysis for correlation and communities (mPFC only)
unthreshComm_PFC_halves_plot <- lapply(seq_along(unthreshComm_PFC_halves_plot), function(x) cbind(unthreshComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
D1 <- unthreshComm_PFC_halves_plot
D2 <- lapply(unthreshComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
Data <- c(D1,D2)
subjList_halves_plot <- rep(best$SubjID, each = 2)
allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))
```

@@

# Compare correlation with community approach on mPFC
tempComm <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, unthreshComm_PFC_halves[[x+1]]$FiedlerVec))
tempCor <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
tempBoth <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))
prepostComp <- data.frame(Community = tempComm, Correlation = tempCor, Between = tempBoth)
prepostComp <- melt(prepostComp)
colnames(prepostComp) <- c("Approach", "Correlation")
prepostComp_permTest <- permute(tempComm, tempCor, paired = T)
prepostComp_ES <- cohenD(tempComm, tempCor)
```

@@

### *Table 1. (UPDATE) Significant brain regions per literature*
| Literature                  | Significant Brain Regions   |
| :-------------------------- | --------------------------: |
| Default Mode Network        | `r paste(dmnLbls)`          |
| Subjective Value            | `r paste(valLbls)`          |

@@

``` {r Stability per subject: PCC vs mPFC (Fig 10), fig.align="center", fig.width=5, fig.height=4, fig.cap = "Figure 10. ARI between each window and the original pattern for PCC and mPFC separately (left), and the mean per-subject ARI for the whole group (middle). Regardless of the mean ARI, standard deviation remained low for both regions (right).", echo=FALSE, message = FALSE, cache = TRUE}

# # plots
# SC_PCCPFC_plot <- ggplot(data = SC_PCC)
# SC_PCCPFC_plot <- SC_PCCPFC_plot + geom_line(aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[2], alpha = 0.3, show.legend = F) +
#   geom_smooth(aes(x = Window, y = Index), color = Cols[2], fill = Cols[2]) +
#   ylim(0,1) + 
#   labs(y = "ARI") +
#   theme(text = element_text(size=35)) +
#   geom_line(data = SC_PFC, aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[1], alpha = 0.3, show.legend = F) +
#   geom_smooth(data = SC_PFC, aes(x = Window, y = Index), color = Cols[1], fill = Cols[1]) +
#   theme_classic()

@@

grid.arrange(SC_PCCPFC_mean_plot, SC_PCCPFC_sd_plot, ncol = 2)
